---
title: "Hw04"
author: '107035165'
date: "3/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
firm_data1 = read.csv('3firmExample_data3.csv')
str(firm_data1)
firm_data1$date
```
library(xts)
library(PerformanceAnalytics)
date1 = as.Date(firm_data1[,1], "%Y/%m/%d")
#convert firm_data1 into time series data: xts
firm_data1.xts = as.xts(firm_data1[,-1], order.by = date1)
firm.data1<-coredata(firm_data1.xts)
summary(firm.data1)
skewness(firm.data1)
rbind(apply(firm.data1, 2, summary),
      apply(firm.data1, 2, skewness),
      apply(firm.data1, 2, kurtosis))

#====================================================================================
# IF you know the ticker of stocks, then you can 
# download directly from yahoo finance
#=====================================================================================
```{r}
library(plyr)
library(quantmod)
tickers<-c("JWN", "SBUX", "MSFT")
data.env<-new.env()
# here we use l_ply so that we don't double save the data
# getSymbols() does this already so we just want to be memory efficient
# go through every stock and try to use getSymbols()
l_ply(tickers, function(sym) try(getSymbols(sym, env=data.env), silent=T))
# now we only want the stocks that got stored from getSymbols()
# basically we drop all "bad" tickers
stocks <- tickers[tickers %in% ls(data.env)]
# now we just loop through and merge our good stocks
# if you prefer to use an lapply version here, that is also fine
# since now we are just collecting all the good stock xts() objects
data <- xts()
# i=1
for(i in seq_along(stocks)) {
  symbol <- stocks[i]
  data <- merge(data, Ad(get(symbol, envir=data.env)))
}
head(data)
str(data)
# convert POSIXct into date series
data<-xts(coredata(data), order.by = as.Date(index(data), tz=""))
head(data)
tail(data)
```
#=================================
# Minimum variance portfolio
#=================================
```{r}
library(fBasics)
Sigma = cov(firm_data1[,2:4])
std = sqrt(diag(Sigma))
ones = rep(1,3)     
one.vec = matrix(ones, ncol=1)
a = inv(Sigma)%*%one.vec
b = t(one.vec)%*%a
mvp.w =a / as.numeric(b)
mvp.w
mvp.ret<-sum((mvp.w)*colMeans(firm_data1[,2:4]))

mvp.ret
```
#==================================
# Assume return is specified as 0.06.  
# Try to find its optimal weight and standard deviation (tangency portfolio), 
# expected return and Sharpe ratio.
#=================================
```{r}
mu<-0.06/12
return <- firm_data1[,2:4]
Ax <- rbind(2*cov(return), colMeans(return), rep(1, ncol(return)))
Ax <- cbind(Ax, rbind(t(tail(Ax, 2)), matrix(0, 2, 2)))
b0 <- c(rep(0, ncol(return)), mu, 1)
out<-solve(Ax, b0)
wgt<-out[1:3]
wgt
sum(wgt)
ret.out<-sum(wgt*colMeans(return))
ret.out.annual<-ret.out*12
ret.out.annual
std.out<-sqrt(t(wgt)%*%cov(return)%*%wgt)
std.out.annual<-std.out*sqrt(12)
std.out.annual
```
#====================================================================================================
# Or write your own function to find min var for a  specified return mu;
# Reference: Introduction to R for Quantitative Finance: Chapter 2, p31
# Solve a diverse range of problems with R, one of the most powerful tools for quantitative finance
#====================================================================================================
```{r}
return = firm_data1[,2:4]
#specified portfolio return: mu
mu=0.06/12
minvariance <- function(return, mu) {
  #return <- log(tail(assets, -1) / head(assets, -1))
  Ax <- rbind(2*cov(return), colMeans(return), rep(1, ncol(return)))
  Ax <- cbind(Ax, rbind(t(tail(Ax, 2)), matrix(0, 2, 2)))
  b0 <- c(rep(0, ncol(return)), mu, 1)
 zx<-solve(Ax, b0)
 weight<-zx[1:ncol(return)]
 ret.out<-sum(weight*colMeans(return))
 std.out<-sqrt(t(wgt)%*%cov(return)%*%wgt)
 list(weight=weight, rtn=ret.out, sd=std.out)
}

minvariance(return, mu)
```
#======================================================
# Create frontier function to plot efficient frontier
#======================================================
```{r}
frontier <- function(return){
  #return <- log(tail(assets, -1) / head(assets, -1))
  n = ncol(return)
  Q = cov(return)
  Ax <- rbind(2*cov(return), colMeans(return), rep(1, n))
  Ax <- cbind(Ax, rbind(t(tail(Ax, 2)), matrix(0, 2, 2)))
  r <- colMeans(return)
  rbase <- seq(min(r), max(r), length = 100)
  s <- sapply(rbase, function(x) {
    b0 <- c(rep(0, ncol(return)), x, 1)
    y <- head(solve(Ax, b0), n)
    sqrt(y%*%Q%*%y)
  })
  plot(s, rbase, xlab = 'Std', ylab = 'Return')
}

frontier(return)
```

```{r}
#library(timeSeries)
return = firm_data1[,2:4]
# convert data to timeseries
ret.ts<- timeSeries(return, date1)
chart.CumReturns(ret.ts, legend.loc = 'topleft', main = '')

plot(portfolioFrontier(ret.ts))
```

```{r}
install.packages("rugarch", dependencies=TRUE)
install.packages("PerformanceAnalytics", dependencies=TRUE)
install.packages("fAssets", dependencies=TRUE)
install.packages("fPortfolio",dependencies=TRUE)
```





